Project 2

### 2021-10-08 project_2.Rmd
Emotion tables

>>>>

```{r emotion_words}
emotion_list <- read_csv("emotion_list.txt")
emotion_words <- tibble(emotion_list, emotion = TRUE)
```

```{r hemingway_emotions}
hemingway_emotions <- tidy_hemingway %>% left_join(emotion_words)
```

```{r fitzgerald_emotions}
fitzgerald_emotions <- tidy_fitzgerald %>% left_join(emotion_words)
```

```{r fitzgerald_emotion_table}
#counting how often female words appeared
#table shows each text and the respective percentage
fitzgerald_emotion_calc <- fitzgerald_emotions %>% group_by(title) %>% count(emotion) %>% mutate(percent = n/sum(n)*100)

```{r hemingway_emotion_table}
#counting how often female words appeared
#table shows each text and the respective percentage
hemingway_emotion_calc <- hemingway_emotions %>% group_by(title) %>% count(emotion) %>% mutate(percent = n/sum(n)*100)
